The effect of climate forcing on numerical simulations of the Cordilleran Ice Sheet at the Last Glacial Maximum

### 2013-11-18 sections/climate.tex
Update location map
Add geographical names and update colormap.

The spatial distribution of JJA and DJF mean precipitation rates in WorldClim reveals a strong precipitation decline beyond the coastal regions (Fig.~\ref{fig:prec}), primarily as a result of the continuous orographic barrier formed by the Boundary Ranges, the Coast Mountains and the Cascades. A less pronounced precipitation peak is also visible over the interior ranges. From an ice sheet mass balance point of view, these heterogeneities become even stronger due to the difference in timing of the precipitation peak through the year. Whereas coastal regions experience most precipitation as snow during the accumulation season (DJF), inland regions experience dry winters and most of the annual precipitation consequently falls as rain during the ablation season (JJA).

>>>>

The spatial distribution of JJA and DJF mean precipitation rates in WorldClim reveals a strong precipitation decline beyond the coastal regions (Fig.~\ref{fig:prec}), primarily as a result of the continuous orographic barrier formed by the Wrangell and St.-Elias mountains, the Coast Mountains and the Cascades (Fig.~\ref{fig:locmap}). A less pronounced precipitation peak is also visible over the interior ranges. From an ice sheet mass balance point of view, these heterogeneities become even stronger due to the difference in timing of the precipitation peak through the year. Whereas coastal regions experience most precipitation as snow during the accumulation season (DJF), inland regions experience dry winters and most of the annual precipitation consequently falls as rain during the ablation season (JJA).
